AD Target Gene Report

### 2020-02-19 code/03-Run.Rmd
Module2
Total Catchup

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable
configuration <- "configs/M62.yaml"
config <- read_yaml(file=paste0('./',configuration))

@@

  source('code/modules/02-DiffExp_module.R')

>>>>

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(file=paste0('./',configuration))

@@

  source('code/modules/02-DiffExpression_module.R')
